Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-11-29 paper/reply.tex
replace $C_d{z}$ by $C_d(z)$ in Formula (2)

6) Some noticed TYPOS
- Page 2, formula (2), it should be $C_d(z)$ instead of $C_dz$
- Page 2, Line 4 from right bottom, there is one redundant ``system''
- Page 4, in Sect 3.3 the line below formula S(z)=$a_0$ $z^N$ + $...$, the rows and columns of Jury matrix M should be (2N-2)xN instead of (2N2)xN
- Figure 5 is on the next page of Figure 6, which should be switched.

>>>>

6) Some noticed TYPOS

- Page 2, formula (2), it should be $C_d(z)$ instead of $C_dz$

- Page 2, Line 4 from right bottom, there is one redundant ``system''

- Page 4, in Sect 3.3 the line below formula S(z)=$a_0$ $z^N$ + $...$, the rows and columns of Jury matrix M should be (2N-2)xN instead of (2N2)xN

- Figure 5 is on the next page of Figure 6, which should be switched.
